---
title: "PPC_Data"
author: "BSP"
date: "02/12/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

-------------------------------------------------------------------------------------------------------------------------
This Report demonstrates important Performance parameters for the Blast furnaces in the years 2019,2020,2021 



## Productivity 

Productivity for the purpose of the report is calculated by the formula 



               PRODUCTIVITY = HOT METAL PRODUCTION / USEFUL BF VOLUME 




```{r productivity, include=FALSE}
library(reshape2)
source("~/Data Science using R/Projects/emd/parameters.R")


## melting and reshaping the data for plotting 

Productivity_2019 <- melt(Productivity_2019,id="Months")
Productivity_2019 <- subset(Productivity_2019,!is.na(Productivity_2019$value))
Productivity_2019$Months <- factor(Productivity_2019$Months, levels = Months)

Productivity_2020 <- melt(Productivity_2020,id="Months")
Productivity_2020 <- subset(Productivity_2020,!is.na(Productivity_2020$value))
Productivity_2020$Months <- factor(Productivity_2020$Months, levels = Months)

Productivity_2021 <- melt(Productivity_2021,id="Months")
Productivity_2021 <- subset(Productivity_2021,!is.na(Productivity_2021$value))
Productivity_2021$Months <- factor(Productivity_2021$Months, levels = Months)

```



Graphs for productivity for the year 2019,2020,2021 



```{r productivity_2019 ,echo=FALSE}
library(ggplot2)
ggplot(Productivity_2019,            
                          aes(x = Months,
                              y = value,group=variable,
                              color = variable)) +  geom_line() + ggtitle("Produtivity (T/M3/D) 2019")+theme(plot.title = element_text(hjust = 0.5))
```

```{r productivity_2020 , echo=FALSE}
library(ggplot2)
ggplot(Productivity_2020,            
                          aes(x = Months,
                              y = value,group=variable,
                              color = variable)) +  geom_line() + ggtitle("Produtivity (T/M3/D) 2020")+theme(plot.title = element_text(hjust = 0.5))
```

```{r productivity_2021 ,echo=FALSE}
library(ggplot2)
ggplot(Productivity_2021,            
                          aes(x = Months,
                              y = value,group=variable,
                              color = variable)) +  geom_line() + ggtitle("Produtivity (T/M3/D) 2021")+theme(plot.title = element_text(hjust = 0.5))
```


## Total Production Vs Productivity 


```{r bar1 ,echo=FALSE}
library(reshape2)
source("~/Data Science using R/Projects/emd/parameters.R")


Productivity_2019_bar <-  Hot_metal_prod_2019/Vol_Day_2019
Productivity_2019_bar <- cbind(Months,Productivity_2019_bar)
Productivity_2020_bar <- Hot_metal_prod_2020/Vol_Day_2020
Productivity_2020_bar <- cbind(Months,Productivity_2020_bar[-1,])
Productivity_2021_bar <- Hot_metal_prod_2021/Vol_Day_2021
Productivity_2021_bar <- cbind(Months,Productivity_2021_bar[-1,])


```



```{r bar19 ,echo=FALSE,warning=FALSE}
Total_Prod_2019 <- data.frame(cbind(Months,Hot_metal_prod_2019$SHOP,format(round(Productivity_2019_bar$SHOP,2),nsmall=2)))


names(Total_Prod_2019) <- c("Months","Total Hot Metal Production","Total Productivity")

Total_Prod_2019_plot <- melt(Total_Prod_2019,id="Months")
Total_Prod_2019_plot <- subset(Total_Prod_2019_plot,!is.na(Total_Prod_2019_plot$value))
Total_Prod_2019_plot$Months <- factor(Total_Prod_2019_plot$Months, levels = Months)

ggplot(Total_Prod_2019_plot, aes(x=Months, y=value, fill=variable)) +
  geom_bar(stat='identity', position='dodge')+ ggtitle("2019")+theme(plot.title = element_text(hjust = 0.5))
```
  
  
```{r bar20 ,echo=FALSE,warning=FALSE}
Total_Prod_2020 <- data.frame(cbind(Months,Hot_metal_prod_2020$SHOP,format(round(Productivity_2020_bar$SHOP,2),nsmall=2)))

names(Total_Prod_2020) <- c("Months","Total Hot Metal Production","Total Productivity")

Total_Prod_2020_plot <- melt(Total_Prod_2020[-1,],id="Months")
Total_Prod_2020_plot <- subset(Total_Prod_2020_plot,!is.na(Total_Prod_2020_plot$value))
Total_Prod_2020_plot$Months <- factor(Total_Prod_2020_plot$Months, levels = Months)

ggplot(Total_Prod_2020_plot, aes(x=Months, y=value, fill=variable)) +
  geom_bar(stat='identity', position='dodge')+ ggtitle("2020")+theme(plot.title = element_text(hjust = 0.5))

```

```{r bar21 ,echo=FALSE,warning=FALSE}

Total_Prod_2021 <- data.frame(cbind(Months,Hot_metal_prod_2021$SHOP,format(round(Productivity_2021_bar$SHOP,2),nsmall=2)))

names(Total_Prod_2021) <- c("Months","Total Hot Metal Production","Total Productivity")
Total_Prod_2021 <- subset(Total_Prod_2021 , (Total_Prod_2021$`Total Hot Metal Production` > 0 & Total_Prod_2021$`Total Productivity` > 0)) 
Total_Prod_2021_plot <- melt(Total_Prod_2021[-1,],id="Months")
Total_Prod_2021_plot <- subset(Total_Prod_2021_plot,Total_Prod_2021_plot$value > 0)
Total_Prod_2021_plot$Months <- factor(Total_Prod_2021_plot$Months, levels = Months)

ggplot(Total_Prod_2021_plot, aes(x=Months, y=value, fill=variable)) +
  geom_bar(stat='identity', position='dodge')+ ggtitle("2021")+theme(plot.title = element_text(hjust = 0.5))

```


\newpage

## Coke Rate 

Coke Rate for the purpose of the report is calculated by the formula 



                         Coke Rate = Coke / THM 



```{r coke_rate, include=FALSE}
library(reshape2)
source("~/Data Science using R/Projects/emd/parameters.R")


## melting and reshaping the data for plotting 

Coke_Rate_2019 <- melt(Coke_Rate_2019,id="Months")
Coke_Rate_2019 <- subset(Coke_Rate_2019,!is.na(Coke_Rate_2019$value))
Coke_Rate_2019$Months <- factor(Coke_Rate_2019$Months, levels = Months)

Coke_Rate_2020 <- melt(Coke_Rate_2020,id="Months")
Coke_Rate_2020 <- subset(Coke_Rate_2020,!is.na(Coke_Rate_2020$value))
Coke_Rate_2020$Months <- factor(Coke_Rate_2020$Months, levels = Months)

Coke_Rate_2021 <- melt(Coke_Rate_2021,id="Months")
Coke_Rate_2021 <- subset(Coke_Rate_2021,!is.na(Coke_Rate_2021$value))
Coke_Rate_2021$Months <- factor(Coke_Rate_2021$Months, levels = Months)

```




Graphs for Coke Rate for the year 2019,2020,2021 





```{r Coke_Rate_2019 ,echo=FALSE}
library(ggplot2)
ggplot(Coke_Rate_2019,            
       aes(x = Months,
           y = value,group=variable,
           color = variable)) +  geom_line() + ggtitle("Coke Rate (KG/THM) 2019")+theme(plot.title = element_text(hjust = 0.5))
```

```{r Coke_Rate_2020,echo=FALSE}
library(ggplot2)
ggplot(Coke_Rate_2020,            
       aes(x = Months,
           y = value,group=variable,
           color = variable)) +  geom_line()  + ggtitle("Coke Rate (KG/THM) 2020")+theme(plot.title = element_text(hjust = 0.5))
```

```{r Coke_Rate_2021,echo=FALSE}
library(ggplot2)
ggplot(Coke_Rate_2021,            
       aes(x = Months,
           y = value,group=variable,
           color = variable)) +  geom_line() + ggtitle("Coke Rate (KG/THM) 2021")+theme(plot.title = element_text(hjust = 0.5))
```


## Total Production Vs Coke Rate  


```{r barcr1 ,echo=FALSE}

source("~/Data Science using R/Projects/emd/parameters.R")

library(reshape2)

Coke_Rate_2019_bar <- (Coke_kg_2019/Hot_metal_prod_2019)*1000
Coke_Rate_2019_bar <- cbind(Months,Coke_Rate_2019_bar)
Coke_Rate_2020_bar <- (Coke_kg_2020/Hot_metal_prod_2020)*1000
Coke_Rate_2020_bar <- cbind(Months,Coke_Rate_2020_bar[-1,])
Coke_Rate_2021_bar <- (Coke_kg_2021/Hot_metal_prod_2021)*1000
Coke_Rate_2021_bar <- cbind(Months,Coke_Rate_2021_bar[-1,])



```



```{r barcr19 ,echo=FALSE,warning=FALSE}


x <- Hot_metal_prod_2019$SHOP

Total_CR_2019 <- data.frame(cbind(Months,x/400,format(round(Coke_Rate_2019_bar$SHOP,0),nsmall=0)))


names(Total_CR_2019) <- c("Months","Total Hot Metal Production","Total Coke Rate")

Total_CR_2019_plot <- melt(Total_CR_2019,id="Months")
Total_CR_2019_plot <- subset(Total_CR_2019_plot,!is.na(Total_CR_2019_plot$value))
Total_CR_2019_plot$Months <- factor(Total_CR_2019_plot$Months, levels = Months)
Total_CR_2019_plot$value <- as.numeric(Total_CR_2019_plot$value )
Total_CR_2019_plot <- Total_CR_2019_plot[c(-26,-13),]

ggplot(Total_CR_2019_plot, aes(x=Months, y=value, fill=variable)) +
  geom_bar(stat='identity', position='dodge')+ ggtitle("2019")+theme(plot.title = element_text(hjust = 0.5))


```
  
  
```{r barcr20 ,echo=FALSE,warning=FALSE}
x <- Hot_metal_prod_2020[-1,]$SHOP
Total_CR_2020 <- data.frame(cbind(Months,x/400,format(round(Coke_Rate_2020_bar$SHOP,0),nsmall=0)))

names(Total_CR_2020) <- c("Months","Total Hot Metal Production","Total Coke Rate")

Total_CR_2020_plot <- melt(Total_CR_2020,id="Months")
Total_CR_2020_plot <- subset(Total_CR_2020_plot,!is.na(Total_CR_2020_plot$value))
Total_CR_2020_plot$Months <- factor(Total_CR_2020_plot$Months, levels = Months)
Total_CR_2020_plot$value <- as.numeric(Total_CR_2020_plot$value )


Total_CR_2020_plot <- Total_CR_2020_plot[c(-26,-13),]

ggplot(Total_CR_2020_plot, aes(x=Months, y=value, fill=variable))+
  geom_bar(stat='identity', position='dodge')+ ggtitle("2020")+theme(plot.title = element_text(hjust = 0.5))



```

```{r barcr21 ,echo=FALSE,warning=FALSE}

x <- Hot_metal_prod_2021[-1,]$SHOP
Total_CR_2021 <- data.frame(cbind(Months,x/400,format(round(Coke_Rate_2021_bar$SHOP,0),nsmall=0)))

names(Total_CR_2021) <- c("Months","Total Hot Metal Production","Total Coke Rate")
Total_CR_2021 <- subset(Total_CR_2021 , (Total_CR_2021$`Total Hot Metal Production` > 0 & Total_CR_2021$`Total Coke Rate`> 0)) 
Total_CR_2021_plot <- melt(Total_CR_2021,id="Months")
Total_CR_2021_plot <- subset(Total_CR_2021_plot,Total_CR_2021_plot$value > 0)
Total_CR_2021_plot$Months <- factor(Total_CR_2021_plot$Months, levels = Months)
Total_CR_2021_plot$value <- as.numeric(Total_CR_2021_plot$value )


Total_CR_2021_plot <- Total_CR_2021_plot[c(-8,-16),]


ggplot(Total_CR_2021_plot, aes(x=Months, y=value, fill=variable)) +
  geom_bar(stat='identity', position='dodge')+ ggtitle("2021")+theme(plot.title = element_text(hjust = 0.5))

```




\newpage

## CDI RATE 

CDI Rate for the purpose of the report is calculated by the formula 



                                 CDI Rate = CDI / THM 




```{r CDI_Rate ,include=FALSE}

library(reshape2)
source("~/Data Science using R/Projects/emd/parameters.R")


## melting and reshaping the data for plotting 

CDI_Rate_2019 <- melt(CDI_Rate_2019,id="Months")
CDI_Rate_2019 <- subset(CDI_Rate_2019,!is.na(CDI_Rate_2019$value))
CDI_Rate_2019$Months <- factor(CDI_Rate_2019$Months, levels = Months)

CDI_Rate_2020 <- melt(CDI_Rate_2020,id="Months")
CDI_Rate_2020 <- subset(CDI_Rate_2020,!is.na(CDI_Rate_2020$value))
CDI_Rate_2020$Months <- factor(CDI_Rate_2020$Months, levels = Months)


CDI_Rate_2021 <- melt(CDI_Rate_2021,id="Months")
CDI_Rate_2021 <- subset(CDI_Rate_2021,!is.na(CDI_Rate_2021$value))
CDI_Rate_2021$Months <- factor(CDI_Rate_2021$Months, levels = Months)
```





Graphs for CDI Rate for the year 2019,2020,2021




```{r CDI_Rate_2019,echo=FALSE}
library(ggplot2)
ggplot(CDI_Rate_2019,            
       aes(x = Months,
           y = value,group=variable,
           color = variable)) +  geom_line() + ggtitle("CDI Rate (KG/THM) 2019")+theme(plot.title = element_text(hjust = 0.5))
```

```{r CDI_Rate_2020,echo=FALSE}
library(ggplot2)
ggplot(CDI_Rate_2020,            
       aes(x = Months,
           y = value,group=variable,
           color = variable)) +  geom_line() + ggtitle("CDI Rate (KG/THM) 2020")+theme(plot.title = element_text(hjust = 0.5))
```

```{r CDI_Rate_2021,echo=FALSE}
library(ggplot2)
ggplot(CDI_Rate_2021,            
       aes(x = Months,
           y = value,group=variable,
           color = variable)) +  geom_line() + ggtitle("CDI Rate (KG/THM) 2021")+theme(plot.title = element_text(hjust = 0.5))
```

## Total Production Vs CDI Rate  


```{r barcd1 ,echo=FALSE}

source("~/Data Science using R/Projects/emd/parameters.R")

library(reshape2)

CDI_Rate_2019_bar <-  (CDI_kg_2019/Hot_metal_prod_2019)*1000
CDI_Rate_2019_bar <- cbind(Months,CDI_Rate_2019_bar)
CDI_Rate_2020_bar <-  (CDI_kg_2020/Hot_metal_prod_2020)*1000
CDI_Rate_2020_bar <- cbind(Months,CDI_Rate_2020_bar[-1,])
CDI_Rate_2021_bar <-  (CDI_kg_2021/Hot_metal_prod_2021)*1000
CDI_Rate_2021_bar <- cbind(Months,CDI_Rate_2021_bar[-1,])




```



```{r barcd19 ,echo=FALSE,warning=FALSE , include=FALSE}
Total_CDI_2019 <- data.frame(cbind(Months,Hot_metal_prod_2019$SHOP,format(round(CDI_Rate_2019_bar$SHOP,0),nsmall=0)))


names(Total_CDI_2019) <- c("Months","Total Hot Metal Production","Total Coke Rate")

Total_CDI_2019_plot <- melt(Total_CDI_2019,id="Months")
Total_CDI_2019_plot <- subset(Total_CDI_2019_plot,!is.na(Total_CDI_2019_plot$value))
Total_CDI_2019_plot$Months <- factor(Total_CDI_2019_plot$Months, levels = Months)

ggplot(Total_CDI_2019_plot, aes(x=Months, y=value, fill=variable)) +
  geom_bar(stat='identity', position='dodge')+ ggtitle("2019")+theme(plot.title = element_text(hjust = 0.5))



```
  
  
```{r barcd20 ,echo=FALSE,warning=FALSE,include=FALSE}

Total_CDI_2020 <- data.frame(cbind(Months,Hot_metal_prod_2020$SHOP,format(round(CDI_Rate_2020_bar$SHOP,0),nsmall=0)))

names(Total_CDI_2020) <- c("Months","Total Hot Metal Production","Total Coke Rate")

Total_CDI_2020_plot <- melt(Total_CDI_2020[-1,],id="Months")
Total_CDI_2020_plot <- subset(Total_CDI_2020_plot,!is.na(Total_CDI_2020_plot$value))
Total_CDI_2020_plot$Months <- factor(Total_CDI_2020_plot$Months, levels = Months)

ggplot(Total_CDI_2020_plot, aes(x=Months, y=value, fill=variable)) +
  geom_bar(stat='identity', position='dodge')+ ggtitle("2020")+theme(plot.title = element_text(hjust = 0.5))


```

```{r barcd21 ,echo=FALSE,warning=FALSE , include=FALSE}
Total_CDI_2021 <- data.frame(cbind(Months,Hot_metal_prod_2021$SHOP,format(round(CDI_Rate_2021_bar$SHOP,0),nsmall=0)))

names(Total_CDI_2021) <- c("Months","Total Hot Metal Production","Total CDI Rate")
Total_CDI_2021 <- subset(Total_CDI_2021,(! Total_CDI_2021$`Total CDI Rate` == "NaN" & ! Total_CDI_2021$`Total Hot Metal Production` == 0 ))
Total_CDI_2021_plot <- melt(Total_CDI_2021[-1,],id="Months")
Total_CDI_2021_plot$Months <- factor(Total_CDI_2021_plot$Months, levels = Months)

ggplot(Total_CDI_2021_plot, aes(x=Months, y=value, fill=variable)) +
  geom_bar(stat='identity', position='dodge')+ ggtitle("2021")+theme(plot.title = element_text(hjust = 0.5))

```




\newpage

## Nut Coke Rate 


Nut Coke Rate for the purpose of the report is calculated by the formula 



                                 Nut Coke Rate = Nut Coke / THM 



```{r Nut_Coke, include=FALSE}
library(reshape2)
source("~/Data Science using R/Projects/emd/parameters.R")


## melting and reshaping the data for plotting 

Nut_Coke_Rate_2019 <- melt(Nut_Coke_Rate_2019,id="Months")
Nut_Coke_Rate_2019 <- subset(Nut_Coke_Rate_2019,!is.na(Nut_Coke_Rate_2019$value))
Nut_Coke_Rate_2019$Months <- factor(Nut_Coke_Rate_2019$Months, levels = Months)

Nut_Coke_Rate_2020 <- melt(Nut_Coke_Rate_2020,id="Months")
Nut_Coke_Rate_2020 <- subset(Nut_Coke_Rate_2020,!is.na(Nut_Coke_Rate_2020$value))
Nut_Coke_Rate_2020$Months <- factor(Nut_Coke_Rate_2020$Months, levels = Months)

Nut_Coke_Rate_2021 <- melt(Nut_Coke_Rate_2021,id="Months")
Nut_Coke_Rate_2021 <- subset(Nut_Coke_Rate_2021,!is.na(Nut_Coke_Rate_2021$value))
Nut_Coke_Rate_2021$Months <- factor(Nut_Coke_Rate_2021$Months, levels = Months)
```





Graphs for Nut Coke Rate for the year 2019,2020,2021




```{r Nut_Coke_Rate_2019,echo=FALSE}
library(ggplot2)
ggplot(Nut_Coke_Rate_2019,            
       aes(x = Months,
           y = value,group=variable,
           color = variable)) +  geom_line() + ggtitle("Nut Coke Rate (KG/THM) 2019")+theme(plot.title = element_text(hjust = 0.5))
```

```{r Nut_Coke_Rate_2020,echo=FALSE}
library(ggplot2)
ggplot(Nut_Coke_Rate_2020,            
       aes(x = Months,
           y = value,group=variable,
           color = variable)) +  geom_line() + ggtitle("Nut Coke Rate (KG/THM) 2020")+theme(plot.title = element_text(hjust = 0.5))
```

```{r Nut_Coke_Rate_2021,echo=FALSE}
library(ggplot2)
ggplot(Nut_Coke_Rate_2021,            
       aes(x = Months,
           y = value,group=variable,
           color = variable)) +  geom_line() + ggtitle("Nut Coke Rate (KG/THM) 2021")+theme(plot.title = element_text(hjust = 0.5))
```


## Total Production Vs CDI Rate  


```{r barNRC1 ,echo=FALSE}

source("~/Data Science using R/Projects/emd/parameters.R")

library(reshape2)






```



```{r barNRC19 ,echo=FALSE,warning=FALSE}



```
  
  
```{r barNRC20 ,echo=FALSE,warning=FALSE}




```

```{r barNRC21 ,echo=FALSE,warning=FALSE}



```



\newpage
 
## Fuel Rate

Fuel Rate for the purpose of the report is calculated by the formula 



                                Fuel Rate = Coke Rate + CDI Rate + Nut Coke Rate 



```{r Fuel_Rate, include=FALSE}
library(reshape2)
source("~/Data Science using R/Projects/emd/parameters.R")


## melting and reshaping the data for plotting 

Fuel_Rate_2019 <- melt(Fuel_Rate_2019,id="Months")
Fuel_Rate_2019 <- subset(Fuel_Rate_2019,!is.na(Fuel_Rate_2019$value))
Fuel_Rate_2019$Months <- factor(Fuel_Rate_2019$Months, levels = Months)

Fuel_Rate_2020 <- melt(Fuel_Rate_2020,id="Months")
Fuel_Rate_2020 <- subset(Fuel_Rate_2020,!is.na(Fuel_Rate_2020$value))
Fuel_Rate_2020$Months <- factor(Fuel_Rate_2020$Months, levels = Months)

Fuel_Rate_2021 <- melt(Fuel_Rate_2021,id="Months")
Fuel_Rate_2021 <- subset(Fuel_Rate_2021,!is.na(Fuel_Rate_2021$value))
Fuel_Rate_2021$Months <- factor(Fuel_Rate_2021$Months, levels = Months)
```




Graphs for Fuel Rate for the year 2019,2020,2021




```{r Fuel_Rate_2019,echo=FALSE}
library(ggplot2)
ggplot(Fuel_Rate_2019,            
       aes(x = Months,
           y = value,group=variable,
           color = variable)) +  geom_line() + ggtitle("Fuel Rate (KG/THM) 2019")+theme(plot.title = element_text(hjust = 0.5))
```

```{r Fuel_Rate_2020,echo=FALSE}
library(ggplot2)
ggplot(Fuel_Rate_2020,            
       aes(x = Months,
           y = value,group=variable,
           color = variable)) +  geom_line() + ggtitle("Fuel Rate (KG/THM) 2020")+theme(plot.title = element_text(hjust = 0.5))
```

```{r Fuel_Rate_2021,echo=FALSE}
library(ggplot2)
ggplot(Fuel_Rate_2021,            
       aes(x = Months,
           y = value,group=variable,
           color = variable)) +  geom_line() + ggtitle("Fuel Rate (KG/THM) 2021")+theme(plot.title = element_text(hjust = 0.5))
```
## Total Production Vs CDI Rate  


```{r barFR1 ,echo=FALSE}

source("~/Data Science using R/Projects/emd/parameters.R")

library(reshape2)






```



```{r barFR19 ,echo=FALSE,warning=FALSE}



```
  
  
```{r barFR20 ,echo=FALSE,warning=FALSE}




```

```{r barFR21 ,echo=FALSE,warning=FALSE}



```


PS:Some of the Blast furnaces were not operational during the calculation of the data and hence the gaps. 
